\section{Results and Discussion}
\label{sec:results}

\subsection{LCA Comparison}

The Sustainable Minds LCA comparison (Section~\ref{sec:lca}) yielded a total environmental impact of \textbf{30\,mPts} for the reference Air Bar NEX design and \textbf{18\,mPts} for the DfD concept---a \textbf{40\% overall improvement}. Table~\ref{tab:lca_results} summarizes the impact category breakdown.

\begin{table}[H]
\centering
\caption{LCA impact category comparison: Reference vs.\ DfD Concept (percentage contribution to total impact score).}
\label{tab:lca_results}
\begin{tabular}{@{}lcc@{}}
\toprule
\textbf{Impact Category} & \textbf{Reference (\%)} & \textbf{DfD Concept (\%)} \\
\midrule
Carcinogenics              & 62.62 & 42.0 \\
Global Warming             & 8.84  & 9.01 \\
Acidification              & 5.21  & 8.02 \\
Fossil Fuel Depletion      & 5.41  & 6.87 \\
Respiratory Effects        & 4.65  & 6.47 \\
Ecotoxicity                & 4.64  & 5.36 \\
Eutrophication             & 3.62  & 5.80 \\
Non-Carcinogenics          & 3.73  & 7.54 \\
Smog                       & 1.26  & 1.26 \\
\midrule
\textbf{Total (mPts)}     & \textbf{30}  & \textbf{18} \\
\bottomrule
\end{tabular}
\end{table}

The dominant improvement came from switching the aluminum housing from primary to recycled (secondary) aluminum, which drastically reduced the carcinogenics impact associated with primary aluminum smelting. A dedicated LCA for the alternative concept (universal battery standard) was not performed; however, the additional battery-reuse benefit would further reduce per-device impacts by amortizing battery manufacturing across multiple use cycles.

\subsection{Disassembly Performance}

\begin{table}[H]
\centering
\caption{Disassembly performance metrics.}
\label{tab:disassembly_results}
\begin{tabular}{@{}lccc@{}}
\toprule
\textbf{Metric} & \textbf{Reference} & \textbf{DfD Concept} & \textbf{Alternative} \\
\midrule
Battery removal steps     & $\sim$10           & 1          & 1 \\
Battery removal time      & 10--15 min         & $<$5 sec   & $<$5 sec \\
Full disassembly steps    & $\sim$10           & $\leq$5    & $\leq$5 \\
Full disassembly time     & 10--15 min         & $<$30 sec  & $<$30 sec \\
Tools required            & X-acto knife       & None       & None \\
Destructive?              & Yes                & No         & No \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Material Recovery Analysis}

\begin{table}[H]
\centering
\caption{Estimated material recovery rates by design concept.}
\label{tab:recovery}
\begin{tabular}{@{}lccc@{}}
\toprule
\textbf{Material} & \textbf{Reference} & \textbf{DfD Concept} & \textbf{Alternative} \\
\midrule
Lithium          & $\sim$0\% & $>$90\% & $>$95\% (reuse + recycle) \\
Cobalt/Nickel    & $\sim$0\% & $>$90\% & $>$95\% \\
Copper           & $\sim$0\% & $\sim$80\% & $\sim$85\% \\
Aluminum         & $\sim$0\% & $\sim$85\% & N/A (PP housing) \\
Plastics         & $\sim$0\% & $\sim$50\% & $>$80\% (mono-material) \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Cost Implications}

\begin{itemize}
    \item \textbf{Additional manufacturing cost}: There may be an increase in upfront manufacturing cost due to the incorporation of the snap-fit inserts and their inclusion, (this process requires the creation of new injection molds or CNC lathing depending on the specific component). However, the battery and the cartridge being replaceable will reduce the need for the total number of housing components that need to be manufactured over an extended period of time, potentially reducing overall cost (an LCC and NPV calculation would be able to verify this). 
    \item \textbf{Material savings}: Battery reuse reduces per-device battery cost. If battery is reused 10 times, battery cost per device drops by $\sim$90\%.
    \item \textbf{Regulatory compliance}: DfD design preemptively meets EU Batteries Regulation 2027 requirements, avoiding future redesign costs.
    \item \textbf{Waste management savings}: Reduced fire risk and simplified recycling lower municipal waste processing costs.
\end{itemize}

\subsection{Discussion}


\begin{itemize}
    \item The inclusion of a recycled aluminum for the housing showed the greatest amount of reduction in the overall environmental impact, however, our proposed changes for snap-fit inserts to make the design more replacable would also likely increase the lifespan of the product while reducing the impact. 
    \item Being able to replace the battery + cartridges will add to the overall use time of a product, and will increase the duration of their lifespan. 
    \item There would likely be some barriers to the adoption of this new design. Having a snap-fit design would likely require additional manufacturing steps that could add an initial upfront cost.Additionally, the implementation of a return program/QR code system will require company infrastructure to support this, (the same is true for replaceable cartridges/batteries). 
    \item This redesign would align with the recent EU Batteries Regulation, and could be a viable alternative to a total discontinuation of the product. 
    \item Limitations: assumptions in LCA modeling, idealized recycling rates, consumer participation uncertainty
\end{itemize}
