\section{Conclusions}
\label{sec:conclusions}


This project analyzed the environmental impact of disposable electronic cigarettes and applied Design for Disassembly principles to redesign the product for improved end-of-life management. The key findings are:

\begin{enumerate}
    \item Finding 1: Current disposable e-cigarettes are designed as sealed, single-use units that prevent any material recovery. The LCA showed that carcinogens were the highest impact factor, accounting for 62.6\% of the total impact score, which we were able to significantly reduce by changing the housing material to a recycled aluminum alternative.

    \item Finding 2: The product was not at all designed for disassembly, being thoroughly sealed together with a thick layer of adhesive. Changing our design to include snap-fit components for the housing, quick-disconnect wires for the battery, and a sliding cartridge for the E-liquid container would significantly improve the ability of the user to replace specific components individually, reducing the amount of E-waste, (and fires), caused by individuals throwing away fully assembled vapes with a partially charged battery still inside. The ability to disassemble the product would ideally reduce mixed waste, as it would make it easier to separate into it's individual components, making it easier to recycle.

    \item Finding 3: The proposed Universal Removable Battery Standard, defining three standardized battery sizes with mechanical and electrical interface specifications, could reduce per-device environmental impact by enabling battery reuse across multiple device lifecycles.

    \item Finding 4: By using recycled (secondary) aluminum for the shell instead of primary aluminum, the alternative design achieved a \textbf{40\% reduction} in overall environmental impact (30\,mPts to 18\,mPts), making the housing material swap the single most effective design change identified in the LCA.

    \item Finding 4: By using a lighter aluminum material for the shell, the alternative design has a lower environmental impact than the original not only in reducing carcinogens, but also in the manufacturing and transportation processes, via Sustainable Minds.
    
\end{enumerate}

The proposed standard aligns with the EU Batteries Regulation (2023/1542), which will require removable and replaceable batteries in all portable electronics by February 2027. Early adoption of such a standard would provide manufacturers with a compliance pathway while addressing the urgent environmental and safety concerns associated with the current generation of disposable e-cigarettes.

\subsection{Limitations}

\begin{itemize}
    \item Certain LCA assumptions had to be made, (including the type of PCB/solder used, the specific type of epoxy used, etc.), as they were not included within the product spec sheet.
    \item Our redesign requires a large, upfront manufacturing cost to design and create more snap-fit designs, as well as the implementation of quick disconnect wires.
    \item There is some consumer behavior uncertainty (will users actually remove batteries?)
    \item We discussed the urgency of the need for these design changes, as the EU is pushing for further regulation, but how will other countries/territories respond? If they do not push for the same level of regulation, there may not be a sense of urgency to implement these design changes. 
    \item Our design would likely increase the lifespan of our products, meaning that there is a potential to extend the lifecycle of nicotine products (public health consideration)
\end{itemize}

\subsection{Future Work}
\begin{itemize}
    \item Prototype fabrication and physical disassembly testing
    \item Consumer behavior studies on battery removal compliance
    \item Detailed cost--benefit analysis for manufacturers
    \item Engagement with standards bodies (IEC, ISO) for formal standardization
    \item Extension to rechargeable/refillable e-cigarette designs
\end{itemize}
